\pagenumbering{arabic}
\section{INTRODUCTION}
\setstretch{1.5}
\subsection{Background}
The search for rental rooms has traditionally been a time-consuming and frustrating endeavor. With the rise of digital technologies, online platforms have emerged to address this challenge. However, many existing rental room finder platforms lack user-friendly interfaces, accurate information, and personalized recommendations. These shortcomings often lead to suboptimal matches between renters and available rooms. Our project builds upon the evolving landscape of digital solutions to create a rental room finder that prioritizes user needs, transparency, and convenience.

\subsection{Problem Statement}
Finding the perfect rental room has become a challenge. One needs to surf over all the town, ask locals for the available room. Walking all day to find room is to much hectic process.Whether you're a student seeking a quiet place for focused studying, a young professional starting a new chapter in a  city, or an adventurer exploring a new locale, the search for the ideal living space can be both exciting and overwhelming.So our "Rental Room finder" is your ultimate solution for effortless and efficient rental room discovery.



\subsection{Scope}
This project will focus on developing a web-based application for rental room finder. The application will have interface for users to search for rental rooms based on their preferences, such as location, budget, facilities, and room types. The platform will also incorporate contract system to provide users with legal contract and prevent  risk of scam. . Additionally, the application will facilitate direct communication between users and property owners, enabling seamless interactions and information exchange. The scope also includes the implementation of secure user profiles and a database to store accommodation details.\\


\subsection{Objective}

\begin{itemize}
    \item Develop an intuitive and responsive web-based application for users to search, compare, and select rental rooms.
    \item Enable direct communication between Customer and Owners 
    

  
\end{itemize}
