\section{FEASIBILITY STUDY}
\subsection{Economic Feasibility}
Economical feasibility is a crucial aspect of any project, including the development of a rental room finder. The costs associated with developing and maintaining the platform must be weighed against the potential benefits and returns. The initial investment in software development, user interface design, database management, and server hosting needs to be carefully evaluated. Additionally, the project's impact on cost savings for users, who would spend less time and effort searching for accommodations, contributes to its overall economic viability.The MERN stack offers a seamless and cost-effective approach to building a dynamic and responsive application, ensuring a high-quality user experience while minimizing development expenses.The use of open-source tools eliminates substantial licensing costs, making our project economically viable.
\subsection{Operational Feasibility}
Operational feasibility for the "Rental Room Finder" web app is driven by key factors like user-friendliness, Criteria Customization, and Sercure legal process. Its UI is user friendly. The app's interface is designed to be intuitive, ensuring users can easily navigate without advanced technical knowledge. Maintenance and support are expected to be straightforward, reducing the need for complex technical assistance. Overall, the "Rental Room Finder" web app is operationally feasible, offering a ultimate solution for effortless and efficient rental room discovery.

\subsection{Technical Feasibility}
The "Rental Room Finder" web app utilizes the MERN (MongoDB, Express.js, React, Node.js) stack for technical feasibility. React and Node.js are used for frontend and backend development, respectively. These technologies are well-established with substantial backing from reputable organizations which ensures the availability of extensive technical support within the development community.Additionally, compatibility with various devices and operating systems, as well as the ability to handle potential traffic spikes, will be evaluated to ensure the platform's technical feasibility. Therefore, the "Rental Room Finder" project is technically feasible with rich well-supported technologies.




